Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-17 paper/sw-contract.tex
Update text in paper to match contract changes.

guarantee "Waypoints coincide with air vehicle locations": *\label{line:sw-guarantee-1}*
  wp => avl;
guarantee "Starts include a new waypoint" : *\label{line:sw-guarantee-2}*
  strt => wp;
guarantee "Waypoints are well-formed" :  *\label{line:sw-guarantee-3}*
  wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Starts within one cycle of requests if not alerting" : *\label{line:sw-guarantee-4}*
  (strt => ((not alrt) and req)) -> 
  (strt => ((not alrt) and (req or pre(req))));
guarantee "Alert if not started within one cycle of requests" : *\label{line:sw-guarantee-5}*
  true -> ((pre(req and not strt) and not strt) => alrt);
guarantee "Once alerted always alerted" : *\label{line:sw-guarantee-6}*
  true -> (pre(alrt) => alrt);
\end{lstlisting}
\end{lrbox}

@@

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
\lineref{line:sw-guarantee-6} ensures that once alerted always alerted since an alert in the pre-state requires an alert in the post-state., \texttt{\textbf{Once}(alrt) \textbf{and} alrt}.
These six guarantees define the behavior of the SW component under the three assumptions.

>>>>

guarantee "Waypoints coincide with air vehicle locations": *\label{line:sw-guarantee-1}*
  wp => avl;
guarantee "Starts include a new waypoint" : *\label{line:sw-guarantee-2}*
  strt => wp;
guarantee "Waypoints are well-formed" :  *\label{line:sw-guarantee-3}*
  wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Starts within one cycle of requests if not alerting" : *\label{line:sw-guarantee-4}*
  (strt => ((not alrt) and req)) -> 
  (strt => ((not alrt) and (req or pre(req))));
guarantee "Alert if not started within one cycle of requests" : *\label{line:sw-guarantee-5}*
  true -> ((pre(req and not strt) and not strt) => alrt);
guarantee "Once alerted always alerted" : *\label{line:sw-guarantee-6}*
  Once(alrt) => alrt;
\end{lstlisting}
\end{lrbox}

@@

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
The last guarantee ensures that alert is persistent.
The \texttt{Once} operator is true if the enclosed expression has ever been true before the current moment.
\lineref{line:sw-guarantee-6} ensures if alert has ever happened in the past, then it is happening in the present moment.
These six guarantees define the behavior of the SW component under the three assumptions.
